---
title: "Gapminder - data manipulation"
author: "YOUR NAME"
output: html_document
---

Throughout this lesson and the next, we will use `gapminder` dataset which is available in an R package of the same name. The `gapminder` dataframe tracks demographic data in countries of the world over time. 

Let's load the packages in our interactive environment by running the following code chunk in the Console.

```{r load-pkg, include = FALSE}
library(tidyverse)        #for data verbs/ggplot
library(gapminder)        #for data
```

### Warm Up

To learn more about the data set, you can bring up the help file with `?gapminder`. Let's also load the data using `data` and take a look at it in the spreadsheet editor.

Take a look at the variable types  with the `glimpse` function.

## Exercises


### Exercise 1.

Use `filter` to extract the data for Canada and then select the variables country, continent, year, and lifeExp.


```{r exercise1}


```

### Exercise 2.

Which countries had a life expectancy below 50 years of age in 2007? Count the number of countries.

```{r exercise2}


```

### Exercise 3.

Which country had the higher life expectancy in 1977: Ireland or Brazil? 

```{r ex3}


```


### Exercise 4.

Does the result of the following code surprise you? How do the select helpers deal with case by default? Type `?contains` in the Console to see how to override the default and then try it.

```{r ex4}

gapminder %>% select( contains("POP") )

```


### Exercise 5.

Sort the countries by life expectancy (in descending order) to find the ones with the highest life expectancy.  Use the function `slice_head` from at the end of the pipeline to just print the first five rows.  


### Exercise 6.

Create a new variable called `gdp` which recovers each country's GDP by multiplying the population and GDP per capita. What do you notice about where the new variable is located?


## Exercise 7.

How many unique countries does the data set contain? (note: distinct drops the other variables by default)

## Exercise 8.

How many unique countries are in Asia? 


