---
title: "Introduction to R"
author: "YOUR Name"
output: html_document
---


### Instructions
+ This homework is due on Monday July 11 by 1:10 pm. No late work is accepted unless prior arrangements have been made with the instructor.
+ Please answer ALL questions (including those that do not involve R) in the locations marked in this template. Remember to periodically **knit** your document to check that the output appears as you want it to; you will be turning in your knit html document. 
+ You will need to upload this document in CANVAS. Take a look at the material from Week 1: Hello World for instructions on exporting your files from JupyterHub and into CANVAS.
+  Please answer the questions in the order in which they are posed. Write in complete sentences, and support your answers where asked. 


**These questions are from Introduction to Data Science by Rafael Irizarry**

1.  The formula for the sum of the squares of the first $n$ natural numbers is $$\frac{n  (n+1) (2n +1)}{6}.$$ 
Use this to calculate the sum of the squares of the first 100 natural numbers by filling in the partial code given below.  (Don't forget to remove the comment hash `#` so the code is actually evaluated.)

```{r problem1, echo=T, eval=T}

#n<-
#sum_sq_100<-

```

2. Now use the same formula to calculate the sum of the first 1,000 positive integers. Create a code chunk, give it a name, set `echo=T` and `eval=T` and then type your code and run it.

3. Suppose a high school student asks for help solving a quadratic equation of the form $$ ax^2 + bx +c = 0. $$ The quadratic equation formula gives the solutions as 

$$ \frac{1}{2a} (-b - \sqrt{ b^2 - 4 ac} ),\: \frac{1}{2a} (-b + \sqrt{ b^2 - 4 ac} ).$$ 


  Calculate the solutions for the equation $x^2 + x -1 = 0$ by filling in the partial code given below.  (Don't forget to remove the comment hash `#` so the code is actually evaluated.)

```{r problem3, echo=T,eval=T}

#a <- 
#b <- 
#c <-
#solution_1<-
##solution_2 <-
```


4. In math and programming, we say that we evaluate a function when we replace an argument with a given number. So if we type `sqrt(4)`, we are evaluating the square root function in R.  Use one line of code to compute the log, in base 10, of the square root of 125. (*Hint* use the help `?log` in the console window to get started.)

```{r problem4, echo=T, eval=T}


```
