---
title: "Visualizing Starwars Characters"
author: "YOUR Name"
output: html_document
---

### Instructions
+ This homework is due on Monday July 18 by 1:10 pm. No late work is accepted unless prior arrangements have been made with the instructor.
+ Please answer ALL questions (including those that do not involve R) in the locations marked in this template. Remember to periodically **knit** your document to check that the output appears as you want it to; you will be turning in your knit html document. 
+ You will need to upload this document in CANVAS. Take a look at the material from Week 1: Hello World for instructions on exporting your files from JupyterHub and into CANVAS. 
+  Please answer the questions in the order in which they are posed. Write in complete sentences, and support your answers where asked. 



For this homework, we will practice making different visualizations for the `starwars` data set from the **openintro** package. Let's load the packages we need. 


```{r load-packages, include=FALSE}
library(ggplot2)    #for making graphs
library(openintro)  #for the data
```

Take a look at the `starwars` dataset like we did in class by typing `data(starwars)` at the prompt in the Console pane. 

Then answer the questions below.

1. How many observations are in this dataframe? Who/what is the individual? (That is, who/what is the data being collected on?)

2. How many variables are in this data? Write three variable names (your choice).

3. Modify the following plot to change the color of all points to `"pink"`.

```{r scatterplot}
ggplot(starwars, 
       aes(x = height, y = mass)) + 
  geom_point()
```

3.  Add labels for title, x and y axes, and size of points. Uncomment to see the effect.

```{r scatterplot-labels}
ggplot(starwars, 
       aes(x = height, y = mass)) +
  geom_point() +
  labs(
    #title = "___",
    #x = "___", 
    #y = "___",
    )
```

4.  Pick a single numerical variable and make a histogram of it. Select a reasonable binwidth for it.

(A little bit of starter code is provided below, and the code chunk is set to not be evaluated with `eval: false` because the current code in there is not valid code and hence the document wouldn't knit. Once you replace the code with valid code, set the chunk option to `eval= TRUE`, or remove the `eval` option altogether since it's set to `true` by default.)

```{r histogram, eval = FALSE}
ggplot(starwars, aes(___)) +
  geom___
```

5.  Pick a numerical variable and a categorical variable and make a visualization (you pick the type!) to visualization the relationship between the two variables. 

```{r num-cat}
#| label: num-cat
```


6.  Pick a single categorical variable from the data set and make a bar plot of its distribution.

```{r barplot}
#| label: barplot
```

7.  Pick two categorical variables and make a visualization to visualize the relationship between the two variables. Along with your code and output, provide an interpretation of the visualization.

```{r cat-cat}
#| label: cat-cat
```
