---
title: "Visualizing Starwars Characters"
author: "YOUR Name"
output: html_document
---

### Instructions
+ This homework is due on Monday July 18 by 11:59 pm. No late work is accepted unless prior arrangements have been made with the instructor.
+ Please answer ALL questions (including those that do not involve R) in the locations marked in this template. Remember to periodically **knit** your document to check that the output appears as you want it to; you will be turning in your knit html document. 
+ You will need to upload this document in CANVAS. Take a look at the material from Week 1: Hello World for instructions on exporting your files from JupyterHub and into CANVAS. 
+  Please answer the questions in the order in which they are posed. Write in complete sentences, and support your answers where asked. 



For this homework, we will practice making different visualizations for the `starwars` data set from the **dplyr** package. Let's load the packages we need. 


```{r load-packages, include=FALSE}
library(ggplot2)    #for making graphs
library(dplyr)  #for the data
```

Take a look at the `starwars` dataset like we did in class. 

Then answer the questions below.

1. How many observations are in this data frame? Who/what is the individual? Answer in complete sentences below. 


2. Modify the following code to 
        - change the color of all points to pink!
        - add a title, subtitle, labels for x and y axis and also a caption indicating the source of the data.

```{r scatterplot}
ggplot(starwars, 
       aes(x = height, y = mass)) + 
  geom_point() 
```


3.  Pick a single numerical variable and make a histogram of it. If the histogram looks too jagged with the default binwidth, play around it to make it look smoother. 


4.  Pick a numerical variable and a categorical variable and make a visualization (you pick the type!) of the relationship between the two variables. 

5.  Make a segmented bar chart to visualize the relationship between `sex` and `gender`. 

