---
title: "Airbnb listings in Edinburgh"
author: "YOUR Name"
output: html_document
---

### Instructions
+ This homework is due on Friday Aug 5 by 11:59 pm. No late work is accepted unless prior arrangements have been made with the instructor.
+ Please answer ALL questions (including those that do not involve R) in the locations marked in this template. Remember to periodically **knit** your document to check that the output appears as you want it to; you will be turning in your knit html document. 
+ You will need to upload this document in CANVAS. Take a look at the material from Week 1: Hello World for instructions on exporting your files from JupyterHub and into CANVAS. 
+  Please answer the questions in the order in which they are posed. Write in complete sentences, and support your answers where asked. 



For this homework, we will explore the airbnb listings in Edinburgh, Scotland. The data set is called `edibnb` and is in the package **dsbox**. In addition, we will be using the **tidyverse** suite of packages for plotting and data wrangling and also the **ggridges** package to make density ridge plots.

Let's load the packages we will need.

```{r load-packages, include=FALSE}
library(tidyverse)                 #umbrella package 
library(dsbox)                     #for the data
library(ggridges)                  #for cool density ridge plots
```

**Warm up** View the data in your spreadsheet viewer and also learn about the data by checking out the associated help pages.

## Exercises

1. What does each row in the data set represent? Write a sentence with the answer.   (Hint: think carefully about WHAT/WHO is being described and clearly state it)

2. How many unique neighborhoods are in this data set? Write code and also answer in a sentence. 

You may have noticed from exercise 2 that some rows are missing the name of  neighborhood and instead are listed as `NA` which is R for missing value. Let's go ahead and remove these rows before continuing with the remaining analyses.

The function `is.na()` takes as its argument the variable you want checked for missing values. For example `is.na(neighbourhood)` identifies the rows where the neighbourhood is missing. 
  
3. Fill in the blank and then run the code chunk below to only keep the listings where the neighbourhood is mentioned. Don't forget to delete `eval = FALSE` when you are done.

```{r remove-na, eval = FALSE}
edibnb <- edibnb %>% 
              ___(!is.na(neighbourhood) )   

```


4. Create a density ridge plot comparing Airbnb prices across neighbourhoods. Describe (in your OWN words) the shape of the distributions: is it symmetric, skewed to the right,skewed to the left, bi-modal?  (Don't forget labels, titles)


5. Based on the shape of the price distribution, should you report the mean or median price as a typical price for the neighbourhood? Make a choice and then go ahead and calculate it for each neighbourhood using `group_by` and `summarise`. Be sure to also calculate the standard deviation if reporting the mean or the IQR if reporting the median. 



6. Create a boxplot to compare the distribution of review scores (`review_scores_rating`) across the neighbourhoods. Do the reviews tend to be positive or negative? (Don't forget labels, titles)
 
